\papertitle

### 2012-10-12 manuscript.tex
more text

%----------------------------------------------------------------------------%
\subsection{Ornithopter Attitude Control}

We gathered the data for the experiment by integrating the output of
H$^2$Bird's on-board gyroscope data. We then used
MATLAB\footnote{\url{http://www.mathworks.com/products/matlab/}} to fit a
simple low-order model (Eq.~\ref{eq:transfer_func}) of the turning
behavior to the step response with the physical heading as the state and the
heading set point as the input. This model serves as a simplification of both
the turning dynamics of the ornithopter and the on-board PID-based attitude
controller. We use this model in Section~\ref{sec:visual_servoing} to
determine the backwards reachable region for navigating through narrow
passages.

@@

We determined the turning speed and turning radius of the H$^2$Bird
experimentally using the response of the system to the step input of a
clockwise 90 degree turn. To measure the response of the system, we recorded
the angular position data of the ornithopter calculated from the on-board
gyroscope data.

@@

In total, 80 trials were run over a variety of starting positions. The goal of our experiments was to verify the model described in~\ref{sec:system_model}, so we conducted 60 of the 80 trials in a grid along the edges of the camera viewplane in 0.05 meter increments from the window to determine the success rate on the edges of the testing space. We conducted 20 additional trials directly in front of the camera to determine the success rate near the center of the testing space. The H$^2$Bird battery was changed approximately every 5 tests, adding more variation to the H$^2$Bird performance by affecting the motor power output.

% Don't think this goes here
Variations in the H$^2$Bird hand launch caused the system to respond 
differently for similar initial conditions. In addition, the H$^2$Bird 
battery was changed approximately every 5 tests, adding more variation to
the H$^2$Bird performance by affecting the motor power output. The effects of 
these noisy factors is considered in Section ~\ref{sec:performance}.
% Might move

@@

We depict the results of this experiment in
Figure~\ref{fig:step_response}.

@@

The step response rise time is approximately 1.4 seconds. The H$^2$Bird
flies at an average forward velocity of 1.2 m/s, so the estimated minimum
turning radius of the robot is 1.07 meters. In experiments, we choose a flight
speed lower than the maximum speed of the ornithopter, to facilitate more
robust tracking.

@@

@@

The geometrically infeasible region is computed using the minimum
turning radius and the geometry of the camera's field-of-view. Both the 
regions in red and blue indicate the infeasible region determined in simulation. 
We ran a simulation on a motion model similar to Dubin's car in ~\cite{lavalle:planning}, with the
angular heading as the input rather than the angular velocity. We used the
turning model, described in Section~\ref{sec:flight_control}, as the input to
the motion model, with a PID controller steering the entire system to the
center of the passage as the input to the tuning model.

We determine the backwards reachable set of initial states for successful
narrow passage traversal both geometrically and in simulation 
(Fig.~\ref{fig:feasible_set}). For the initial conditions, we use a uniform 
grid of 0.05 meter increments within the camera viewing region, and an 
initial angular position perpendicular to the narrow passage plane.

The infeasible region
calculated in simulation is a superset of the geometrically infeasible region.
The simulation is more realistic as the rotational damping during the turn and
the on-board PID controller cause the real system to react to inputs at a
non-constant angular velocity.

The results of the experiments are shown in
Figures~\ref{fig:flight_paths} and~\ref{fig:flight_paths_feasible}.

For initial conditions in the middle of the feasible region and in front of
the camera, we achieved a success rate of 80\%. This case is depicted in
Figure~\ref{fig:flight_paths_feasible}. As we moved towards the edges of the
feasible region in Figure~\ref{fig:flight_paths}, the success rate diminishes
because of several factors. On the edges of the camera frame, the yaw control
inputs are large in magnitude, although this is not necessary in all cases.
Since the control algorithm we are using has no notion of depth, it applies
the same control input whether the ornithopter is close to the camera, where
small changes in heading are adequate, or far away from the camera, where
large changes in heading are necessary. Due to this phenomenon, the controller
often over- or under-compensates in certain regions, depending upon the PID
tuning and the distance from the camera. Tracking noise can also cause passage
negotiation to fail.

>>>>

%----------------------------------------------------------------------------%
\subsection{Ornithopter Attitude Control}
\label{sec:model_attitude}

To model the yaw motion of the ornithopter, we developed a one-dimensional model using the physical heading angle as the output and the heading angle set by the ground station as the input. This model accounts for both the yaw dynamics of the ornithopter and the internal PID controller on the actuator inputs for the tail rotor. We decided upon a one-dimensional model to reduce the complexity of the overall model and enable simple angle inputs and outputs, which is similar to our methods during experiementation. The format of the model we decided up on is shown in Equation~\ref{eq:plain_model}.

\begin{equation}
\label{eq:plain_model}
H(s) = \frac{K}{1 + Rs}
\end{equation}

To model the translational position of the ornithopter, we used a form of Dubin's car model~\cite{lavalle:planning} with the angular position, $\theta$ as an input rather than a state. So the overall motion of the system can be modeled as shown in Equation~\ref{eq:total_model_plain}, where $\theta$ is the time domain output of (\ref{eq:plain_model}) with the angular setpoint provided by the ground station as the input.

\begin{equation}
\label{eq:total_model_plain}
\begin{aligned}
& \dot{x} = sin(\theta)\\
& \dot{y} = cos(\theta)\\
\end{aligned}
\end{equation}

@@

We determined the turning speed and turning radius of the H$^2$Bird
experimentally using the response of the system to the step input of a
clockwise 90 degree turn. To measure the response of the system, we recorded
the angular position data of the ornithopter calculated from the on-board
gyroscope data. We then used
MATLAB\footnote{\url{http://www.mathworks.com/products/matlab/}} to fit a
simple low-order model to the step response as discussed in Section~\ref{sec:model_attitude}.

@@

In total, 80 trials were run over a variety of starting positions. The goal of
our experiments was to verify the model described in
Secttion~\ref{sec:system_model}, so we conducted 60 of the 80 trials in a grid
along the edges of the camera viewplane in 0.05 meter increments from the
window to determine the success rate on the edges of the testing space. We
conducted 20 additional trials directly in front of the camera to determine
the success rate near the center of the testing space. After every 5 trials,
we replaced the current battery with a fully charged one.

@@

The results of the step response experiment are described in
Figure~\ref{fig:step_response}. The first-order model that we fit to the
response is in Equation~\ref{eq:transfer_func}.

@@

The step response rise time is 1.4 seconds. The H$^2$Bird flies
at an average forward velocity of 1.2 m/s during our experiments, so the
estimated minimum turning radius of the robot is 1.07 maters, as described in
Equation~\ref{eq:min_radius}. In the experiments, we choose a flight speed
lower than the maximum speed of the ornithopter, to facilitate more robust
tracking.

\begin{equation}
\label{eq:min_radius}
\begin{aligned}
\text{Minimum radius} & = \frac{360^{\circ}*\text{Rise time}*\text{Flight speed}}{\text{Final angle}*2*\pi}\\
& = \frac{360^{\circ}*1.4s*1.2\frac{m}{s}}{90^{\circ}*2*\pi} = 1.07 m
\end{aligned}
\end{equation}

@@

The results of our experimental trials are shown in
Figures~\ref{fig:flight_paths} and~\ref{fig:flight_paths_feasible}. For
initial conditions in the middle of the testing space and in front of the
camera, we achieved a success rate of 80\%. This case is depicted in
Figure~\ref{fig:flight_paths_feasible}. As we moved towards the edges of the
feasible region in Figure~\ref{fig:flight_paths}, the success rate diminishes
to 50\% because of several factors. On the edges of the camera frame, the yaw
control inputs are large in magnitude, although this is not necessary in all
cases. Since the control algorithm we are using has no notion of depth, it
applies the same control input whether the ornithopter is close to the camera,
where small changes in heading are adequate, or far away from the camera,
where large changes in heading are necessary. Due to this phenomenon, the
controller often over- or under-compensates in certain regions, depending upon
the PID tuning and the distance from the camera. Tracking noise can also cause
passage negotiation to fail. Variations in the H$^2$Bird hand launch can cause
the system to respond differently for similar initial conditions. In addition,
the H$^2$Bird battery was changed approximately every 5 tests, adding more
variation to the H$^2$Bird performance by affecting the motor power output.

@@

We simulated the motion of the ornithopter beginning from certain positional
and angular initial conditions using several components representing the
experimental layout of our system described in Figure~\ref{fig:block_diagram}.
For the "ornithopter dynamics" block, we used the translational model
described by~\ref{eq:total_model_plain} with the angular position model
described by~\ref{eq:transfer_func}. We tuned the PID controller for the
simulation so that paths from known positions looked similar to the behavior
we observed in the experimental data. We also inlcuded the camera capture and
pose estimation delays, and the PID controller sampling rate in the
simulation.

We determine the backwards reachable set of initial states for successful
narrow passage traversal both geometrically and in simulation
(Fig.~\ref{fig:feasible_set}). For the initial conditions, we use a uniform
grid of 0.05 meter increments within the camera viewing region, and an initial
angular position perpendicular to the narrow passage plane. The geometrically
infeasible region is computed using the minimum turning radius and the
geometry of the camera's field-of-view and is indicated in blue. Both the
regions in red and blue indicate the infeasible region determined in
simulation. The feasible region is highlighted in green. A success consisted
of a path that intersects the window at some point and does not leave the
camera viewing triangle. Figure~\ref{fig:feasible_set} is validated by our
experimenal data, as there are no successes within the geometrically
infeasible region. There are a few successes near the boundary of the
infeasible region determined in simulation, but this phenomenon canbe
explained by the results in Figure~\ref{fig:heat_map}.

Figure~\ref{fig:heat_map} depicts the results of a Monte Carlo method of
simulating possible paths of the H$^2$Bird during our experiments. For each
point within a 0.2 meter grid within the camera viewing triangle, we simulated
10 trials using an initial heading randomly sampled from a uniform
distribution between -90$^{\circ}$ and 90$^{\circ}$. As shown in the figure,
there is a region in the middle with a 100\% probability of success, which is
a subset of the feasible region presented in Figure~\ref{fig:feasible_set}.
Along the edges of the camera viewing triangle, however, the probability of
success decreases.

The results of our experimental trials verify the results of the Monte Carlo
simulation of the model that we used. The trials that we conducted in
Figure~\ref{fig:flight_paths_feasible} correspond to the circled region in
Figure~\ref{heat_map}. The 80\% success rate that we experienced in the
experiments corroborates our calculated probability of success of
approximately 80\%. Additionally the diminished success rate of 50\% near the edges of the viewing triangle that we determined through experimentation supports the reduced probability of success calculated by the simulation.
